Landscape composition and beneficial insects

### 2020-06-26 manuscript/manuscript_outline.Rmd
Added a bit to Discussion.
- Need to check covergence of P. distincta model

* We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded to landscape composition, _Phalangium opilio_ did not
  + _P. melanarius_ was influenced by grassland/wetland, pasture, trees/shrubs, pulses, and urban land cover
  + _P. distincta_ was influenced by grassland/wetland, canola, pulses, and urban land cover
  + _P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover
  + Finally, _P. opilio_ was weakly influenced by pasture, and trees/shrubs
  + These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab))

@@

+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Cover class     | _P. melanarius_            | _P. distincta_             | _P. moesta_                 | _P. opilio_           |
+=================+============================+============================+=============================+=======================+
| Grass/ Wetland  | - Local sink (late)        |                            | - Local sink                | - Local sink (early)  |
|                 |                            |                            | - Landscape source          |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Canola          | - Local source (early)     | - _Local source (early)_   | - Local source (early)      |                       |
|                 | - Landscape sink (early)   | - _Local sink (late)_      | - Local sink (late)         |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Pasture         |                            | - Landscape sink           |                             |                       | 
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Trees/Shrubland |                            | - Overall sink (late)      | - _Overall source (early)_  | - Local sink (early)  |
|                 |                            |                            | - _Overall sink (late)_     |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Pulses          | - Overall source (late)    |                            | - Landscape source          |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Flax            | - Local sink               |                            |                             | - Overall sink        |
|                 | - Landscape sink           |                            |                             |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Urban           |                            |                            | - Local source (early)      |                       |
|                 |                            |                            | - Local sink (early)        |                       |
|                 |                            |                            | - Landscape sink (late)     |                       |
|                 |                            |                            | - Landscape source (late)   |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+

@@

* The Lycosid spiders _Pardosa distincta_ and _Pardosa moesta_ responded to landscape composition, in particular, pulses, canola, urban, and trees/shrubs 
  + Surprisingly, canola acted as a source for both species, indicating that _Pardosa_ may use canola as foraging grounds
  + @drapela2011 also found that _Pardosa agresti_ had higher activity density in areas with more woody trees and shrubs, as well as in areas close to roadside strips, suggesting similar habitat preferences in both Canadian and European contexts
  +

>>>>

* We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded to landscape composition, _Phalangium opilio_ did not
  + _P. melanarius_ was influenced by grass/wetland, pasture, trees/shrubs, pulses, and urban land cover
  + _P. distincta_ was influenced by grass/wetland, canola, pulses, and urban land cover
  + _P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover
  + Finally, _P. opilio_ was weakly influenced by pasture, and trees/shrubs
  + These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab))

@@

+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Cover class     | _P. melanarius_            | _P. distincta_             | _P. moesta_                 | _P. opilio_           |
+=================+============================+============================+=============================+=======================+
| Grass & Wetland | - Local sink (late)        |                            | - Local sink                | - Local sink (early)  |
|                 |                            |                            | - Landscape source          |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Canola          | - Local source (early)     | - _Local source (early)_   | - Local source (early)      |                       |
|                 | - Landscape sink (early)   | - _Local sink (late)_      | - Local sink (late)         |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Pasture         |                            | - Landscape sink           |                             |                       | 
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Forest & Shrubs |                            | - Overall sink (late)      | - _Overall source (early)_  | - Local sink (early)  |
|                 |                            |                            | - _Overall sink (late)_     |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Pulses          | - Overall source (late)    |                            | - Landscape source          |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Flax            | - Local sink               |                            |                             | - Overall sink        |
|                 | - Landscape sink           |                            |                             |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
| Urban           |                            |                            | - Local source (early)      |                       |
|                 |                            |                            | - Local sink (early)        |                       |
|                 |                            |                            | - Landscape sink (late)     |                       |
|                 |                            |                            | - Landscape source (late)   |                       |
+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+

@@

* The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways
  + Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds
  +

  + @drapela2011 also found that _Pardosa agresti_ had higher activity density in areas with more woody trees and shrubs, as well as in areas close to roadside strips, suggesting similar habitat preferences in both Canadian and European contexts
